\documentclass[a4paper,12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{fancyhdr}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\titleformat{\section}
{\normalfont\Large\bfseries\color{darkblue}}{\thesection}{1em}{}
\titleformat{\subsection}
{\normalfont\large\bfseries\color{darkblue}}{\thesubsection}{1em}{}

\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}

\pagestyle{fancy}
\fancyhf{}
\rhead{ByteHackage Volunteer Manual}
\lhead{Hackathon Management System}
\rfoot{Page \thepage}

\title{\textbf{ByteHackage: Volunteer User Manual}}
\author{Hackathon Management Team}
\date{January 2026}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Introduction}
Welcome to the ByteHackage volunteer team! This manual provides comprehensive instructions on using the Hackathon Management System. As a volunteer, your role is critical in ensuring smooth gate entry, accurate attendance tracking, and timely issue reporting.

\section{Getting Started}

\subsection{Login}
\begin{itemize}
    \item Access the website at the provided URL.
    \item Use your assigned \textbf{username} and \textbf{password}.
    \item Ensure you stay logged in throughout your shift. If logged out, your session-specific locks may be reset.
\end{itemize}

\subsection{Classroom Selection}
\begin{itemize}
    \item Upon login, you will be prompted to select a classroom (e.g., 004, 005, 202, etc.).
    \item \textbf{Important:} You can only select \textbf{one classroom} per session. Once selected, the app will be locked to that room to prevent accidental cross-room updates.
    \item If you need to change your room, you must logout and login again.
\end{itemize}

\section{Key Features}

\subsection{Gate Entry Management}
The Gate Entry page is used during the initial check-in phase.
\begin{itemize}
    \item \textbf{Search:} Use the search bar to find teams by Name, Member Name, or Room Number.
    \item \textbf{Verification Type:} Before marking entry, select the verification method used:
    \begin{itemize}
        \item \textbf{Bonafide:} Official bonafide certificate verified.
        \item \textbf{ID Card:} Student ID card verified.
        \item \textbf{Nothing:} No physical ID verified (not recommended).
    \end{itemize}
    \item \textbf{Individual Toggle:} Tap individual member names to mark them as entered.
    \item \textbf{Team Toggle (Quick Check-in):} Use the slider to mark the entire team as entered.
    \item \textbf{Mark Entry:} The final ``Mark Entry'' button will mark all checked members as present and automatically mark all unchecked members as \textbf{ABSENT}.
\end{itemize}

\subsection{Attendance Management}
Once teams are in their rooms, use the Attendance View.
\begin{itemize}
    \item \textbf{Status Updates:} For each member, you can set the status to:
    \begin{itemize}
        \item \textbf{Present:} Physically in the room.
        \item \textbf{Absent:} Not reported yet.
        \item \textbf{At Lunch:} Currently out for a meal.
        \item \textbf{Sleeping:} Resting in the room/designated area.
        \item \textbf{Left Campus:} Permanently or temporarily left the venue.
    \end{itemize}
    \item \textbf{Quick Attendance Mode:} Use this mode for rapid scanning during rush hours.
    \item \textbf{Real-time Sync:} All updates are saved instantly and visible to coordinators.
\end{itemize}

\subsection{Classroom Status Bar}
Keep the room status updated using the one-tap buttons:
\begin{itemize}
    \item \textbf{Class Active:} Normal hackathon activity.
    \item \textbf{Class at Lunch:} Majority of students are out for food.
    \item \textbf{Night/Sleeping:} Overnight resting period.
    \item \textbf{Emergency/Medical:} Ongoing emergency in the room.
    \item \textbf{Jury/Mentor Visit:} Mentors are currently evaluating teams.
    \item \textbf{Temporarily Empty:} No students currently in the room.
\end{itemize}

\subsection{Issue Reporting}
Report any issues immediately via the ``Report Issue'' page.
\begin{itemize}
    \item \textbf{Categories:} Medical, Technical/WiFi, Power, Food/Water, Security, Discipline/Noise, Equipment.
    \item \textbf{Details:} Provide a brief description of the problem.
    \item \textbf{Tracking:} Coordinators will see these reports instantly on their dashboard.
\end{itemize}

\subsection{Emergency Actions}
For critical situations, use the \textbf{Critical Action} button.
\begin{itemize}
    \item \textbf{Types:} Team Leaving, Team Missing, Emergency, Medical.
    \item \textbf{Notification:} Submitting an emergency alert automatically notifies all 5 predefined organizers.
\end{itemize}

\section{Best Practices}
\begin{itemize}
    \item \textbf{Mobile-First:} The UI is optimized for mobile; use it on your smartphone for flexibility.
    \item \textbf{Save Frequently:} While the system auto-saves, ensure you see the success indicators.
    \item \textbf{Stay Vigilant:} Keep your room status updated to help coordinators manage the event flow.
\end{itemize}

\end{document}
